Joint Training of Classification and Similarity Models for \\ Intention Detection in Task-specific Chatbot

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
modify title
version 7
modified:   paper.tex

\def\year{2021}\relax
%File: formatting-instructions-latex-2021.tex
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai21}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\usepackage{array}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subfigure}
\usepackage{spconf}
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\title{     
  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
  Joint training of classification model and similarity model for low-resource
  text classification in chatbot
}

\begin{document}
  \maketitle

@@

\begin{table*}
    \begin{centering}
      \scalebox{0.9}{
        \begin{tabular}{|c|c|c|c|c|c|}
          \hline 
          \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
          \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
          \hline 
          ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
          \hline 
          Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
          \hline 
          HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
          \hline 
          CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
          \hline 
          BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
          \hline 
        \end{tabular}
      }
      \par
    \end{centering}
    \caption{Statistics for all datasets and few shot settings\footnote{All
    settings of four public datasets would be released to github soon}.}

@@

  \subsection{Datasets}
  Our experiments aim to study the short text classification in the low-resource
  environment  popular  in  the  task-specific conversational chatbot application.
  Hence we choose and configure set datasets to serve this study. Different from
  the  datasets from other short text classification research, such as semantics
  classification  with  very  limited  semantics labels and relatively longer
  input,   the   datasets  adopted  in  our  experiments  are  typically  having
  comparatively  large  number  of  class labels, ranging from several dozens to
  hundreds,  and  each  class  label  is  associated  with  a handful of labeled
  queries with each  query  being usually  one  sentence. Table \ref{tbe:dataset
  statistic} displays their statistics.

@@

  \subsection{Implementation Details}
  For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
  classification  task  and  sentence-pair similarity task. We fine-tune
  our  SFC  system  on  our datasets with max sequence length of 128,
  learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
  of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
  Besides,  we  set  the  max number of the epoch to 100 and save the best model on
  validation  set based on testing result in weighted F1 score (todo: reference). 
  We report the F1 score as the main evaluation measure for all experiments.

@@

  \subsection{Result Analysis}
  All results in F1 score (todo: reference) on the five datasets with different models and configurations are
  showed in Table  \ref{tbe:table2}.

>>>>

\def\year{2021}\relax
%File: formatting-instructions-latex-2021.tex
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai21}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\usepackage{array}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subfigure}
\usepackage[switch]{lineno}
\usepackage{spconf}
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\title{     
  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
  Joint Training of Classification and Similarity Models for \\ 
  Intention Detection in Task-specific Chatbot
}

\begin{document}
  \maketitle
  \linenumbers

@@

\begin{table*}
    \begin{centering}
      \scalebox{0.9}{
        \begin{tabular}{|c|c|c|c|c|c|}
          \hline 
          \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
          \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
          \hline 
          ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
          \hline 
          Amazon-670k & Product review & 250 & 1942 & 8 & 3-fold\tabularnewline
          \hline 
          HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
          \hline 
          CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
          \hline 
          BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
          \hline 
        \end{tabular}
      }
      \par
    \end{centering}
    \caption{Statistics for all datasets and few shot settings.}

@@

  \subsection{Datasets}
  Our experiments aim to study the short text classification in the low-resource
  environment  popular  in  the  task-specific conversational chatbot application.
  Hence we choose and configure set datasets to serve this study. Different from
  the  datasets from other short text classification research, such as semantics
  classification  with  very  limited  semantics labels and relatively longer
  input,   the   datasets  adopted  in  our  experiments  are  typically  having
  comparatively  large  number  of  class labels, ranging from several dozens to
  hundreds,  and  each  class  label  is  associated  with  a handful of labeled
  queries with each  query  being usually  one  sentence. Table \ref{tbe:dataset
  statistic} displays their statistics.  All settings of four public datasets would 
  be released to github soon.

@@

  \subsection{Implementation Details}
  For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
  classification  task  and  sentence-pair similarity task. We fine-tune
  our  SFC  system  on  our datasets with max sequence length of 128,
  learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
  of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.
  Besides,  we  set  the  max number of the epoch to 100 and save the best model on
  validation  set based on testing result in weighted F1 score
  \footnote{In the multi-class and multi-label case, this is the average of the
  F1 score of each class with weighting depending on the numbers in each class.}.
  We report the F1 score as the main evaluation measure for all experiments.

@@

  \subsection{Result Analysis}
  All  results  in  F1  score  on  the  five  datasets with different models and
  configurations are showed in Table \ref{tbe:table2}.
